Calculating the nonequilibrium observable by a speed-boosting technique

### 2013-10-30 writedown/accelerate/main.tex
improve

\noindent
In summary, the CHARMM force field is split in the following way:
\begin{align}
  U(\vect R) = U^\hard(\vect R) + U^\soft(\vect R)
\end{align}
where
\begin{align}
  U^\hard(\vect R) &=
  \sum_{\textrm{bonds}} K_b(b-b_0)^2 +
  \sum_{\textrm{non-bonded}} [\,U_{\vdw}^\hard (r_{ij}) + U_{\dir}^\hard (r_{ij})\,] \\\nonumber
  U^\soft(\vect R) &=
  +\sum_{\textrm{angles}} K_\theta (\theta - \theta_0)^2
  +\sum_{\textrm{Urey-Bradley}} K_{\textrm{UB}} (S - S_0)^2\\\nonumber
  &
  +\sum_{\textrm{dihedrals}} K_\phi( 1+\cos(n\phi - \delta)) 
  +\sum_{\textrm{impropers}} K_\omega (\omega - \omega_0)^2\\ \nonumber
  &
  +\sum_{\textrm{residues}} U_{\textrm{CMAP}}(\phi, \psi) \\
  &
  +\sum_{\textrm{non-bonded}}
  \big[\,U^\soft_{\vdw}(r_{ij})
  + U^\soft_{\dir}(r_{ij})
  + U_{\rec}(r_{ij})\,\big]  
\end{align}
Therefore, the interaction for the accelerated system is
\begin{align}
  \hat U(\vect R) = U^\hard(\vect R) + \alpha\,U^\soft(\vect R)  
\end{align}

@@

\begin{table}
  \centering
  \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lcccc}
    \hline\hline
    $\alpha$ & $w_\vdw$ & $r^\hard_\vdw$ [nm] & $w_\dir$ & $r^\hard_\vdw$ [nm] \\\hline
    2           & 1.00     & 0.0   & 1.00    & 0.0\\
    5           & 1.00     & 0.0   & 0.80    & 0.2\\
    6           & 1.00     & 0.0   & 0.67    & 0.2\\
    \hline\hline
  \end{tabular*}
  \caption{The systems tested and the parameters to split the slow and fast parts of the force.}
  \label{tab:tmp1}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[]{figs/fig-meta05.eps}
  \includegraphics[]{figs/fig-meta05-1.eps}
  \caption{$\alpha = 5$, the probability of different conformations as a function of time.
    In the left plot: Red: $A_1$, green: $A_2$, blue: $B_1$, purple: $B_2$, cyan: $C$.
    In the right plot: Red: $A_1+A_2$, blue: $B_1+B_2$, cyan: $C$.
    The lighter colors denote the reference exact dynamics of the conformations ($\alpha = 1$), while the darker colors denote $\alpha = 5$.}
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{figs/fig-meta08.eps}
  \includegraphics[]{figs/fig-meta08-1.eps}
  \caption{$\alpha = 6$, the probability of different conformations as a function of time.
    In the left plot: Red: $A_1$, green: $A_2$, blue: $B_1$, purple: $B_2$, cyan: $C$.
    In the right plot: Red: $A_1+A_2$, blue: $B_1+B_2$, cyan: $C$.
    The lighter colors denote the reference exact dynamics of the conformations ($\alpha = 1$), while the darker colors denote $\alpha = 6$.}
  \label{fig:tmp3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-5.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-5.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-5.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-5.eps}\\
  \caption{The integrated probability fluxes. $\alpha = 2,4,5,8$.}
  \label{fig:tmp3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-3.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-3.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-3.eps}
  \caption{The integrated probability fluxes. $\alpha = 4,5,8$.}
  \label{fig:tmp3}
\end{figure}

>>>>

\noindent
In summary, the CHARMM force field is split in the following way:
\begin{align}
  U(\vect R) = U^\hard(\vect R) + U^\soft(\vect R)
\end{align}
where
\begin{align}\nonumber
  U^\hard(\vect R) =\,&
  (1 - w_b) \sum_{\textrm{bonds}} K_b(b-b_0)^2 \\\nonumber
  &
  +(1 - w_\theta)\bigg[\sum_{\textrm{angles}} K_\theta (\theta - \theta_0)^2
  +\sum_{\textrm{Urey-Bradley}} K_{\textrm{UB}} (S - S_0)^2\bigg]\\\nonumber
  &
  +\sum_{\textrm{non-bonded}} [\,U_{\vdw}^\hard (r_{ij}) + U_{\dir}^\hard (r_{ij})\,] \\\nonumber
  U^\soft(\vect R) =\,&
  w_b\sum_{\textrm{bonds}} K_b(b-b_0)^2 \\\nonumber
  &
  +w_\theta \bigg[\sum_{\textrm{angles}} K_\theta (\theta - \theta_0)^2
  +\sum_{\textrm{Urey-Bradley}} K_{\textrm{UB}} (S - S_0)^2\bigg]\\\nonumber
  &
  +\sum_{\textrm{dihedrals}} K_\phi( 1+\cos(n\phi - \delta)) 
  +\sum_{\textrm{impropers}} K_\omega (\omega - \omega_0)^2\\ \nonumber
  &
  +\sum_{\textrm{residues}} U_{\textrm{CMAP}}(\phi, \psi) \\
  &
  +\sum_{\textrm{non-bonded}}
  \big[\,U^\soft_{\vdw}(r_{ij})
  + U^\soft_{\dir}(r_{ij})
  + U_{\rec}(r_{ij})\,\big]  
\end{align}
Therefore, the interaction for the accelerated system is
\begin{align}
  \hat U(\vect R) = U^\hard(\vect R) + \alpha\,U^\soft(\vect R)  
\end{align}
The parameters $w_b$ and $w_\theta$ are chosen so that the vibrational
frequency of the bond $ \big[1 + (\alpha - 1) w_b\big]\cdot
K_b(b-b_0)^2 $ and angle $ \big[1 + (\alpha - 1) w_\theta\big]\cdot
\big[K_\theta (\theta - \theta_0)^2 +K_{\textrm{UB}} (S - S_0)^2] $ is
no more than the vibrational frequency of the bond and angle
potentials of water molecule, respectively.

@@

\begin{table}
  \centering
  \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lcccc}
    \hline\hline
    $\alpha$ & $w_\vdw$ & $r^\hard_\vdw$ [nm] & $w_\dir$ & $r^\hard_\vdw$ [nm] \\\hline
    2           & 1.00     & 0.0   & 1.00    & 0.0\\
    4           & 1.00     & 0.0   & 0.88    & 0.2\\
    % 5           & 1.00     & 0.0   & 0.80    & 0.2\\
    % 6           & 1.00     & 0.0   & 0.67    & 0.2\\
    8           & 1.00     & 0.0   & 0.50    & 0.2\\
    \hline\hline
  \end{tabular*}
  \caption{The systems tested and the parameters to split the slow and fast parts of the force.}
  \label{tab:tmp1}
\end{table}

@@

% \begin{figure}
%   \centering
%   \includegraphics[]{figs/fig-meta05.eps}
%   \includegraphics[]{figs/fig-meta05-1.eps}
%   \caption{$\alpha = 5$, the probability of different conformations as a function of time.
%     In the left plot: Red: $A_1$, green: $A_2$, blue: $B_1$, purple: $B_2$, cyan: $C$.
%     In the right plot: Red: $A_1+A_2$, blue: $B_1+B_2$, cyan: $C$.
%     The lighter colors denote the reference exact dynamics of the conformations ($\alpha = 1$), while the darker colors denote $\alpha = 5$.}
%   \label{fig:tmp2}
% \end{figure}

\begin{figure}
  \centering
  \includegraphics[]{figs/fig-meta08.eps}
  \includegraphics[]{figs/fig-meta08-1.eps}
  \caption{$\alpha = 8$, the probability of different conformations as a function of time.
    In the left plot: Red: $A_1$, green: $A_2$, blue: $B_1$, purple: $B_2$, cyan: $C$.
    In the right plot: Red: $A_1+A_2$, blue: $B_1+B_2$, cyan: $C$.
    The lighter colors denote the reference exact dynamics of the conformations ($\alpha = 1$), while the darker colors denote $\alpha = 6$.}
  \label{fig:tmp3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-02-5.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-5.eps}\\
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-2.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-3.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-4.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-5.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-3.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-4.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-5.eps}\\
  \caption{The integrated probability fluxes. $\alpha = 2,4,8$.}
  \label{fig:tmp3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-04-1-3.eps}\\
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-1.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-2.eps}
  % \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-05-1-3.eps}\\
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-1.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-2.eps}
  \includegraphics[width=0.195\textwidth]{figs/fig-meta-iflux-08-1-3.eps}
  \caption{The integrated probability fluxes. $\alpha = 4,8$.}
  \label{fig:tmp3}
\end{figure}
